\subsection{Guest Mode}
Guest Mode is designed for quick, one-time participation without any setup or login. 
It allows users to access a session instantly without any user data being stored. 
When someone joins a session in Guest Mode, the application automatically generates a temporary user identity and stores it locally in the browser. 
This identity helps the system recognize the user during the session. 
Guest users have full access to participate in the session’s activities, but their presence is temporary and not tied to any personal information. 
Once the session ends or the browser is closed, the user effectively disappears from the system’s memory.
This mode is ideal for situations where users are not expected to return.

\subsection{Private Mode}
Private Mode offers a more structured and secure way to connect to a session. 
It is used when a user scans a QR code that links to a specific, private session. 
This link contains a hidden token that identifies the session and grants access to it. 
When the user opens the link, the application uses this token to establish a secure connection with the backend system. 
At the same time, the user's device is assigned a unique identifier, which is stored locally and remains available for future sessions on the same device. 
This allows the system to recognize returning users, maintain a consistent identity across multiple sessions, and apply session-specific rules or roles. 
The connection is verified before granting access — so users without the correct token or link will be blocked.