\chapter{Contributors}

\href{https://github.com/finnkock}{@Finn Kock}: 
\begin{itemize}
	\item Creating UI concept for the mode selection and implementing it
    \begin{itemize}[nosep]
        \item[$\cdot$] Animated Background
	    \item[$\cdot$] Item orientations in the Mode Screen
	    \item[$\cdot$]  Character Designs
	    \item[$\cdot$] Character Rotations on touch and button click
	    \item[$\cdot$] Transparency of character in the back
    \end{itemize}
	\item Implement Icons as buttons
	\item Animating text 
	\begin{itemize}[nosep]
        \item[$\cdot$] Create multiple character reactions
        \item[$\cdot$] Choosing a random character reaction according to the mode each time a question is asked
        \item[$\cdot$] Putting the question in a question box with a precalculated length
        \item[$\cdot$] Textanimation for Questiontext and Answertext
	\end{itemize}
    \item Questionbutton top left in main screen + Clickable Mode text for information 
\end{itemize}

\href{https://github.com/alecasbar}{@Alejandro Castilla}: 
\begin{itemize}
    \item Security Tips on the main screen, fetched from the LLM API, with a fallback mechanism in case of server issues.
    \item End Session screen with performance summary (user statistics and grading) and inactivity handling logic (confirmation pop-up and auto-close).
    \item Spider chart visualization of user performance in percentages, with dynamic splitting in case the user answers questions on too many different topics.
    \item Feedback message fetched from the LLM, encouraging users to use SeQG again to improve in their weaker topics.
    \item Adjustments to several components to ensure proper centering in the demo display.
    \item Backend integration improvements and JSON parsing corrections in the prompts for reliable communication with the LLM.
\end{itemize}

\href{https://github.com/sergioPajuelo}{@Sergio Pajuelo}:
\begin{itemize}
    \item The whole welcome screen when scanning the QR code, including differentiation between modes.
    \item Additional information to the user, such as the consent to process their data (with pop-ups), fetching information, etc.
    \item Each mode's screen after selecting the avatar, including the mode description and animated features, dynamic background, etc.
    \item Answer highlighting in the questions for visual feedback to the user.
    \item Improving the user's visibility of the modes descriptions.
    \item Resizing/redesign of the initial screen components and animations as well as the mode selection one due to problems in the demo display.
\end{itemize}

\href{https://github.com/RobertEggert}{@Robert Eggert}: 
\begin{itemize}
    \item The Whole backend logic, including the LLM API, QR Code and the Anti-Breaching Sessions idea (except the Feedback api call).
    \item File based Routing and the File Cleansing logic.
    \item Most of the State and session management and the Connection/Disconnection logic.
    \item All question Types + overlay
    \item Touch compatability
    \item Configs
\end{itemize}